---
title: "Assignment_4 -- Tidyverse skills -- 10.5"
author: "Anthea Yichen Li"
date: "February 20, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tibble)
library(ggplot2)
library("tidyverse")
```

# Assignment 4 -- Tidyverse skills -- 10.5

### 1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).
```{r q1, eval=FALSE}
is_tibble(mtcars)
class(mtcars)
```


###2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviors cause you frustration?

```{r q2, eval=FALSE}
When using dataframes, the df$x command would give the same result as df[,"xyz"] column. When the df[] command is applied to multiple columns, the result we get would be a data frame instead of two vectors. 
```


###3. If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?
```{r q3, eval=FALSE}
"df[[var]]"
```

### 4. Practice referring to non-syntactic names in the following data frame by:

```{r}
something <- tibble(
  `1` = 1:5,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```
  1. extracting the variable called 1
```{r}
something[["1"]]
```

  2. Plotting a scatterplot of 1 vs 2.
```{r}
ggplot(something, aes(x = `1`, y = `2`)) + geom_point()
```

  3. Creating a new column `3` with is `2` divided by `1`:
```{r}
something[["3"]] <- something[["2"]] / something[["1"]]
```

  4. Renaming the columns to `one`, `two`, and `three`:
```{r}
something_great <- rename(something, one = `1`, two = `2`, three = `3`)
something_great
```

###5. What does tibble::enframe() do? When might you use it?

It converts named vectors to a data frame with names and values
```{r q5, eval=FALSE}
it is used to combine vectors to dataframe with col names 
```

###6. What option controls how many additional column names are printed at the footer of a tibble?

The print function for tibbles is in `print.tbl_df`:
```{r q6, eval=FALSE}
print(.... , n_extra = ...)
we can use n_extra in the tibble print function to control the number of columns printed.
```
